PANCHANGE_data_preprocessing

### 2020-08-11 PANCHANGE_data_preprocessing2020-07-15.Rmd
renamed coping.glad

coping.glad.gad.raw.id <- coping.glad.gad.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.coping = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    startDate.coping.glad = startDate,
    gad.problems_made_difficult_care, # Impairment
    gad.pandemic_felt_feelings, # Comparison to before the pandemic (retro)
    gad.feeling_nervous_anxious_or_on_edge_retro = gad.feeling_nervous_anxious_or_on_edge,
    gad.control_worrying_stop_retro = gad.control_worrying_stop,
    gad.worrying_too_much_about_different_things_retro = gad.worrying_too_much_about_different_things,
    gad.trouble_relaxing_retro = gad.trouble_relaxing,
    gad.sit_restless_hard_retro = gad.sit_restless_hard,
    gad.becoming_easily_annoyed_or_irritable_retro = gad.becoming_easily_annoyed_or_irritable,
    gad.awful_feeling_afraid_happen_retro = gad.awful_feeling_afraid_happen,
    gad.feeling_nervous_anxious_or_on_edge_base = gad.feeling_nervous_anxious_or_on_edge.1,
    gad.control_worrying_stop_base = gad.control_worrying_stop.1,
    gad.worrying_too_much_about_different_things_base = gad.worrying_too_much_about_different_things.1,
    gad.trouble_relaxing_base = gad.trouble_relaxing.1,
    gad.sit_restless_hard_base = gad.sit_restless_hard.1,
    gad.becoming_easily_annoyed_or_irritable_base = gad.becoming_easily_annoyed_or_irritable.1,
    gad.awful_feeling_afraid_happen_base = gad.awful_feeling_afraid_happen.1
  ) %>%
  add_numeric(., exclude = exclude_cols_coping_glad) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(coping.glad.gad.raw.id)
# Inspect colnames
colnames(coping.glad.gad.raw.id)
#Differences
dim(coping.glad.gad.raw)[1]-dim(coping.glad.gad.raw.id)[1]
```

@@

# Calulate total score
gad.scored_items_retro <- scoreItems(keys = gad.items_key_retro,
                                        items = coping.glad.gad.raw.id[gad.items_retro],
                                        totals = TRUE, 
                                        missing = TRUE, 
                                        impute = 'none', 
                                        min = 0, 
                                        max = 3)
# Add in column to tibble
coping.glad.gad.raw.id$gad.sum_score_retro_raw <- gad.scored_items_retro$scores

# Look at values
coping.glad.gad.raw.id %>%
  descr(gad.sum_score_retro_raw,
        stats = "common"
        )
```

@@

# Calulate total score
gad.scored_items_base <- scoreItems(keys = gad.items_key_base,
                                        items = coping.glad.gad.raw.id[gad.items_base],
                                        totals = TRUE, 
                                        missing = TRUE, 
                                        impute = 'none', 
                                        min = 0, 
                                        max = 3)
# Add in column to tibble
coping.glad.gad.raw.id$gad.sum_score_base_raw <- gad.scored_items_base$scores

# Look at values
coping.glad.gad.raw.id %>%
  descr(gad.sum_score_base_raw,
        stats = "common"
        )
```

@@

baseline
```{r coping gad baseline missingness}
coping.glad.gad.raw.id <- coping.glad.gad.raw.id %>%
  mutate(
    na_per_person_gad_base =         # variable for NA per person
      rowSums(                       
        is.na(.[gad.items_base])
      )
  )

coping.glad.gad.raw.id %>%
  freq(na_per_person_gad_base, cumul = F) #have a look at the frequency
```

```{r coping gad retrospective missingness}
coping.glad.gad.raw.id <- coping.glad.gad.raw.id %>%
  mutate(
    na_per_person_gad_retro =         # variable for NA per person
      rowSums(
        is.na(.[gad.items_retro])
      )
  )

coping.glad.gad.raw.id %>%
  freq(na_per_person_gad_retro, cumul = F) #have a look at the frequency
```

```{r coping gad base sum score if missigng items set to NA}
coping.glad.gad.raw.id <- coping.glad.gad.raw.id %>%
  mutate(
    gad.sum_score_base =
      if_else(condition = na_per_person_gad_base > 0,
              true = NA_real_,
              false = gad.sum_score_base_raw,
              missing = NA_real_
      )
  )

coping.glad.gad.raw.id %>%
  descr(gad.sum_score_base_raw, stats = "common")

coping.glad.gad.raw.id %>%
  descr(gad.sum_score_base, stats = "common")
```

```{r coping gad retro sum score if missigng items set to NA}
coping.glad.gad.raw.id <- coping.glad.gad.raw.id %>%
  mutate(
    gad.sum_score_retro =
      if_else(condition = na_per_person_gad_retro > 0,
              true = NA_real_,
              false = gad.sum_score_retro_raw,
              missing = NA_real_
      )
  )

coping.glad.gad.raw.id %>%
  descr(gad.sum_score_retro_raw, stats = "common")

coping.glad.gad.raw.id %>%
  descr(gad.sum_score_retro, stats = "common")
```

```{r coping glad gad head}
head(coping.glad.gad.raw.id)
```

```{r coping glad gad summary 2}
summarytools::dfSummary(
  coping.glad.gad.raw.id,
  graph.col = F,
  valid.col = F,
  labels.col = F)
```

@@

# Calulate total score
pcl.scored_items_retro <- scoreItems(keys = pcl.items_key_retro,
                                     items = coping.glad.pcl.raw.id[pcl.items_retro],
                                     totals = TRUE, 
                                     missing = TRUE, 
                                     impute = 'none', 
                                     min = 0, 
                                     max = 1)
# Add in column to tibble
coping.glad.pcl.raw.id$pcl.sum_score_retro_raw <- pcl.scored_items_retro$scores

# Look at values
coping.glad.pcl.raw.id %>%
  descr(pcl.sum_score_retro_raw,
        stats = "common"
  )
```

@@

# Calulate total score
pcl.scored_items_base <- scoreItems(keys = pcl.items_key_base,
                                    items = coping.glad.pcl.raw.id[pcl.items_base],
                                    totals = TRUE, 
                                    missing = TRUE, 
                                    impute = "none", 
                                    min = 1, 
                                    max = 5)
# Add in column to tibble
coping.glad.pcl.raw.id$pcl.sum_score_base_raw <- pcl.scored_items_base$scores

# Look at values
coping.glad.pcl.raw.id %>%
  descr(pcl.sum_score_base_raw,
        stats = "common"
  )
```

@@

baseline
```{r coping pcl baseline missingness}
coping.glad.pcl.raw.id <- coping.glad.pcl.raw.id %>%
  mutate(
    na_per_person_pcl_base =         # variable for NA per person
      rowSums(                       
        is.na(.[pcl.items_base])
      )
  )

coping.glad.pcl.raw.id %>%
  freq(na_per_person_pcl_base, cumul = F) #have a look at the frequency
```

retrospective
```{r coping pcl retrospective missingness}
coping.glad.pcl.raw.id <- coping.glad.pcl.raw.id %>%
  mutate(
    na_per_person_pcl_retro =         # variable for NA per person
      rowSums(
        is.na(.[pcl.items_retro])
      )
  )

coping.glad.pcl.raw.id %>%
  freq(na_per_person_pcl_retro, cumul = F) #have a look at the frequency
```

```{r coping pcl base sum score if missigng items set to NA}
coping.glad.pcl.raw.id <- coping.glad.pcl.raw.id %>%
  mutate(
    pcl.sum_score_base =
      if_else(condition = na_per_person_pcl_base > 0,
              true = NA_real_,
              false = pcl.sum_score_base_raw,
              missing = NA_real_
      )
  )

coping.glad.pcl.raw.id %>%
  descr(pcl.sum_score_base_raw, stats = "common")

coping.glad.pcl.raw.id %>%
  descr(pcl.sum_score_base, stats = "common")
```

```{r coping pcl retro sum score if missigng items set to NA}
coping.glad.pcl.raw.id <- coping.glad.pcl.raw.id %>%
  mutate(
    pcl.sum_score_retro =
      if_else(condition = na_per_person_pcl_retro > 0,
              true = NA_real_,
              false = pcl.sum_score_retro_raw,
              missing = NA_real_
      )
  )

coping.glad.pcl.raw.id %>%
  descr(pcl.sum_score_retro_raw, stats = "common")

coping.glad.pcl.raw.id %>%
  descr(pcl.sum_score_retro, stats = "common")
```

```{r coping glad pcl head}
head(coping.glad.pcl.raw.id)
```

```{r coping glad pcl summary}
summarytools::dfSummary(
  coping.glad.pcl.raw.id,
  graph.col = F,
  valid.col = F,
  labels.col = F)
```

@@

# Calulate total score
phq.scored_items_retro <- scoreItems(keys = phq.items_key_retro,
                                     items = coping.glad.phq.raw.id[phq.items_retro],
                                     totals = TRUE, 
                                     missing = TRUE, 
                                     impute = 'none', 
                                     min = 0, 
                                     max = 3)
# Add in column to tibble
coping.glad.phq.raw.id$phq.sum_score_retro_raw <- phq.scored_items_retro$scores

# Look at values
coping.glad.phq.raw.id %>%
  descr(phq.sum_score_retro_raw,
        stats = "common"
  )
```

@@

# Calulate total score
phq.scored_items_base <- scoreItems(keys = phq.items_key_base,
                                    items = coping.glad.phq.raw.id[phq.items_base],
                                    totals = TRUE, 
                                    missing = TRUE, 
                                    impute = 'none', 
                                    min = 0, 
                                    max = 3)
# Add in column to tibble
coping.glad.phq.raw.id$phq.sum_score_base_raw <- phq.scored_items_base$scores

# Look at values
coping.glad.phq.raw.id %>%
  descr(phq.sum_score_base_raw,
        stats = "common"
  )
```

@@

retrospective
```{r coping phq retro missingness}
coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
  mutate(
    na_per_person_phq_retro =         # variable for NA per person
      rowSums(
        is.na(.[phq.items_retro])
      )
  )

coping.glad.phq.raw.id %>%
  freq(na_per_person_phq_retro, cumul = F) #have a look at the frequency
```

```{r coping phq retro missingness 8 items}
coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
  mutate(
    phq.missing_only_suicide_item_retro = 
      if_else(
        condition = na_per_person_phq_retro == 1 & 
          is.na(phq.dead_hurting_thoughts_retro_numeric), 
        true = 1,
        false = 0,
        missing = NA_real_
      )
  )

coping.glad.phq.raw.id %>%
  freq(phq.missing_only_suicide_item_retro,
       cumul = F)
```

baseline
```{r coping phq base missingness}
coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
  mutate(
    na_per_person_phq_base =         # variable for NA per person
      rowSums(                       
        is.na(.[phq.items_base])
      )
  )

coping.glad.phq.raw.id %>%
  freq(na_per_person_phq_base, cumul = F) #have a look at the frequency
```

We need to identify those who have all items APART from the suicide ideation item - to still include these individuals. 
```{r coping phq base missingness 8 items}
coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
  mutate(
    phq.missing_only_suicide_item_base = 
      if_else(
        condition = na_per_person_phq_base == 1 & 
          is.na(phq.dead_hurting_thoughts_base_numeric), 
        true = 1,
        false = 0,
        missing = NA_real_
      )
  )

coping.glad.phq.raw.id %>%
  freq(phq.missing_only_suicide_item_base,
       cumul = F)
```

```{r coping phq base sum score if missigng items set to NA}
coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
  mutate(
    phq.sum_score_base =
      if_else(condition = na_per_person_phq_base > 0,
              true = NA_real_,
              false = phq.sum_score_base_raw,
              missing = NA_real_
      )
  )

coping.glad.phq.raw.id %>%
  descr(phq.sum_score_base_raw, stats = "common")

coping.glad.phq.raw.id %>%
  descr(phq.sum_score_base, stats = "common")
```

8 items
```{r phq base sum score if missigng items set to NA - 8 items}
coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
  mutate(
    phq.sum_score_8items_base =
      if_else(condition = na_per_person_phq_base > 1 &
                phq.missing_only_suicide_item_base == 1,
              true = NA_real_,
              false = phq.sum_score_base_raw,
              missing = NA_real_
      )
  )

coping.glad.phq.raw.id %>%
  descr(phq.sum_score_8items_base, stats = "common")
```

```{r coping phq retro sum score if missigng items set to NA}
coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
  mutate(
    phq.sum_score_retro =
      if_else(condition = na_per_person_phq_retro > 0,
              true = NA_real_,
              false = phq.sum_score_retro_raw,
              missing = NA_real_
      )
  )

coping.glad.phq.raw.id %>%
  descr(phq.sum_score_retro_raw, stats = "common")

coping.glad.phq.raw.id %>%
  descr(phq.sum_score_retro, stats = "common")
```

8 items
```{r phq retro sum score if missigng items set to NA - 8 items}
coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
  mutate(
    phq.sum_score_8items_retro =
      if_else(condition = na_per_person_phq_retro > 1 &
                phq.missing_only_suicide_item_retro == 1,
              true = NA_real_,
              false = phq.sum_score_retro_raw,
              missing = NA_real_
      )
  )

coping.glad.phq.raw.id %>%
  descr(phq.sum_score_8items_retro, stats = "common")
```

```{r coping glad phq head}
head(coping.glad.phq.raw.id)
```

```{r coping glad phq summary}
summarytools::dfSummary(
  coping.glad.phq.raw.id,
  graph.col = F,
  valid.col = F,
  labels.col = F)
```

@@

# Calulate total score
ocir.scored_items_retro <- scoreItems(keys = ocir.items_key_retro,
                                     items = coping.glad.ocir.raw.id[ocir.items_retro],
                                     totals = TRUE, 
                                     missing = TRUE, 
                                     impute = 'none', 
                                     min = 0, 
                                     max = 4)
# Add in column to tibble
coping.glad.ocir.raw.id$ocir.sum_score_retro_raw <- ocir.scored_items_retro$scores

# Look at values
coping.glad.ocir.raw.id %>%
  descr(ocir.sum_score_retro_raw,
        stats = "common"
  )
```

@@

# Calulate total score
ocir.scored_items_base <- scoreItems(keys = ocir.items_key_base,
                                    items = coping.glad.ocir.raw.id[ocir.items_base],
                                    totals = TRUE, 
                                    missing = TRUE, 
                                    impute = 'none', 
                                    min = 0, 
                                    max = 4)
# Add in column to tibble
coping.glad.ocir.raw.id$ocir.sum_score_base_raw <- ocir.scored_items_base$scores

# Look at values
coping.glad.ocir.raw.id %>%
  descr(ocir.sum_score_base_raw,
        stats = "common"
  )
```

@@

retrospective
```{r coping ocir retro missingness}
coping.glad.ocir.raw.id <- coping.glad.ocir.raw.id %>%
  mutate(
    na_per_person_ocir_retro =         # variable for NA per person
      rowSums(
        is.na(.[ocir.items_retro])
      )
  )

coping.glad.ocir.raw.id %>%
  freq(na_per_person_ocir_retro, cumul = F) #have a look at the frequency
```

baseline
```{r coping ocir base missingness}
coping.glad.ocir.raw.id <- coping.glad.ocir.raw.id %>%
  mutate(
    na_per_person_ocir_base =         # variable for NA per person
      rowSums(                       
        is.na(.[ocir.items_base])
      )
  )

coping.glad.ocir.raw.id %>%
  freq(na_per_person_ocir_base, cumul = F) #have a look at the frequency
```

```{r coping ocir base sum score if missigng items set to NA}
coping.glad.ocir.raw.id <- coping.glad.ocir.raw.id %>%
  mutate(
    ocir.sum_score_base =
      if_else(condition = na_per_person_ocir_base > 0,
              true = NA_real_,
              false = ocir.sum_score_base_raw,
              missing = NA_real_
      )
  )

coping.glad.ocir.raw.id %>%
  descr(ocir.sum_score_base_raw, stats = "common")

coping.glad.ocir.raw.id %>%
  descr(ocir.sum_score_base, stats = "common")
```

```{r coping ocir retro sum score if missigng items set to NA}
coping.glad.ocir.raw.id <- coping.glad.ocir.raw.id %>%
  mutate(
    ocir.sum_score_retro =
      if_else(condition = na_per_person_ocir_retro > 0,
              true = NA_real_,
              false = ocir.sum_score_retro_raw,
              missing = NA_real_
      )
  )

coping.glad.ocir.raw.id %>%
  descr(ocir.sum_score_retro_raw, stats = "common")

coping.glad.ocir.raw.id %>%
  descr(ocir.sum_score_retro, stats = "common")
```

```{r coping glad ocir head}
head(coping.glad.ocir.raw.id)
```

```{r coping glad ocir summary}
summarytools::dfSummary(
  coping.glad.ocir.raw.id,
  graph.col = F,
  valid.col = F,
  labels.col = F)
```

>>>>

coping.gad.raw.id <- coping.gad.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.coping = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    startDate.coping = startDate,
    gad.problems_made_difficult_care, # Impairment
    gad.pandemic_felt_feelings, # Comparison to before the pandemic (retro)
    gad.feeling_nervous_anxious_or_on_edge_retro = gad.feeling_nervous_anxious_or_on_edge,
    gad.control_worrying_stop_retro = gad.control_worrying_stop,
    gad.worrying_too_much_about_different_things_retro = gad.worrying_too_much_about_different_things,
    gad.trouble_relaxing_retro = gad.trouble_relaxing,
    gad.sit_restless_hard_retro = gad.sit_restless_hard,
    gad.becoming_easily_annoyed_or_irritable_retro = gad.becoming_easily_annoyed_or_irritable,
    gad.awful_feeling_afraid_happen_retro = gad.awful_feeling_afraid_happen,
    gad.feeling_nervous_anxious_or_on_edge_base = gad.feeling_nervous_anxious_or_on_edge.1,
    gad.control_worrying_stop_base = gad.control_worrying_stop.1,
    gad.worrying_too_much_about_different_things_base = gad.worrying_too_much_about_different_things.1,
    gad.trouble_relaxing_base = gad.trouble_relaxing.1,
    gad.sit_restless_hard_base = gad.sit_restless_hard.1,
    gad.becoming_easily_annoyed_or_irritable_base = gad.becoming_easily_annoyed_or_irritable.1,
    gad.awful_feeling_afraid_happen_base = gad.awful_feeling_afraid_happen.1
  ) %>%
  add_numeric(., exclude = exclude_cols_coping_glad) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(coping.gad.raw.id)
# Inspect colnames
colnames(coping.gad.raw.id)
#Differences
dim(coping.gad.raw)[1]-dim(coping.gad.raw.id)[1]
```

@@

# Calulate total score
gad.scored_items_retro <- scoreItems(keys = gad.items_key_retro,
                                        items = coping.gad.raw.id[gad.items_retro],
                                        totals = TRUE, 
                                        missing = TRUE, 
                                        impute = 'none', 
                                        min = 0, 
                                        max = 3)
# Add in column to tibble
coping.gad.raw.id$gad.sum_score_retro_raw <- gad.scored_items_retro$scores

# Look at values
coping.gad.raw.id %>%
  descr(gad.sum_score_retro_raw,
        stats = "common"
        )
```

@@

# Calulate total score
gad.scored_items_base <- scoreItems(keys = gad.items_key_base,
                                        items = coping.gad.raw.id[gad.items_base],
                                        totals = TRUE, 
                                        missing = TRUE, 
                                        impute = 'none', 
                                        min = 0, 
                                        max = 3)
# Add in column to tibble
coping.gad.raw.id$gad.sum_score_base_raw <- gad.scored_items_base$scores

# Look at values
coping.gad.raw.id %>%
  descr(gad.sum_score_base_raw,
        stats = "common"
        )
```

@@

baseline
```{r coping gad baseline missingness}
coping.gad.raw.id <- coping.gad.raw.id %>%
  mutate(
    na_per_person_gad_base =         # variable for NA per person
      rowSums(                       
        is.na(.[gad.items_base])
      )
  )

coping.gad.raw.id %>%
  freq(na_per_person_gad_base, cumul = F) #have a look at the frequency
```

```{r coping gad retrospective missingness}
coping.gad.raw.id <- coping.gad.raw.id %>%
  mutate(
    na_per_person_gad_retro =         # variable for NA per person
      rowSums(
        is.na(.[gad.items_retro])
      )
  )

coping.gad.raw.id %>%
  freq(na_per_person_gad_retro, cumul = F) #have a look at the frequency
```

```{r coping gad base sum score if missigng items set to NA}
coping.gad.raw.id <- coping.gad.raw.id %>%
  mutate(
    gad.sum_score_base =
      if_else(condition = na_per_person_gad_base > 0,
              true = NA_real_,
              false = gad.sum_score_base_raw,
              missing = NA_real_
      )
  )

coping.gad.raw.id %>%
  descr(gad.sum_score_base_raw, stats = "common")

coping.gad.raw.id %>%
  descr(gad.sum_score_base, stats = "common")
```

```{r coping gad retro sum score if missigng items set to NA}
coping.gad.raw.id <- coping.gad.raw.id %>%
  mutate(
    gad.sum_score_retro =
      if_else(condition = na_per_person_gad_retro > 0,
              true = NA_real_,
              false = gad.sum_score_retro_raw,
              missing = NA_real_
      )
  )

coping.gad.raw.id %>%
  descr(gad.sum_score_retro_raw, stats = "common")

coping.gad.raw.id %>%
  descr(gad.sum_score_retro, stats = "common")
```

```{r coping glad gad head}
head(coping.gad.raw.id)
```

```{r coping glad gad summary 2}
summarytools::dfSummary(
  coping.gad.raw.id,
  graph.col = F,
  valid.col = F,
  labels.col = F)
```

@@

# Calulate total score
pcl.scored_items_retro <- scoreItems(keys = pcl.items_key_retro,
                                     items = coping.pcl.raw.id[pcl.items_retro],
                                     totals = TRUE, 
                                     missing = TRUE, 
                                     impute = 'none', 
                                     min = 0, 
                                     max = 1)
# Add in column to tibble
coping.pcl.raw.id$pcl.sum_score_retro_raw <- pcl.scored_items_retro$scores

# Look at values
coping.pcl.raw.id %>%
  descr(pcl.sum_score_retro_raw,
        stats = "common"
  )
```

@@

# Calulate total score
pcl.scored_items_base <- scoreItems(keys = pcl.items_key_base,
                                    items = coping.pcl.raw.id[pcl.items_base],
                                    totals = TRUE, 
                                    missing = TRUE, 
                                    impute = "none", 
                                    min = 1, 
                                    max = 5)
# Add in column to tibble
coping.pcl.raw.id$pcl.sum_score_base_raw <- pcl.scored_items_base$scores

# Look at values
coping.pcl.raw.id %>%
  descr(pcl.sum_score_base_raw,
        stats = "common"
  )
```

@@

baseline
```{r coping pcl baseline missingness}
coping.pcl.raw.id <- coping.pcl.raw.id %>%
  mutate(
    na_per_person_pcl_base =         # variable for NA per person
      rowSums(                       
        is.na(.[pcl.items_base])
      )
  )

coping.pcl.raw.id %>%
  freq(na_per_person_pcl_base, cumul = F) #have a look at the frequency
```

retrospective
```{r coping pcl retrospective missingness}
coping.pcl.raw.id <- coping.pcl.raw.id %>%
  mutate(
    na_per_person_pcl_retro =         # variable for NA per person
      rowSums(
        is.na(.[pcl.items_retro])
      )
  )

coping.pcl.raw.id %>%
  freq(na_per_person_pcl_retro, cumul = F) #have a look at the frequency
```

```{r coping pcl base sum score if missigng items set to NA}
coping.pcl.raw.id <- coping.pcl.raw.id %>%
  mutate(
    pcl.sum_score_base =
      if_else(condition = na_per_person_pcl_base > 0,
              true = NA_real_,
              false = pcl.sum_score_base_raw,
              missing = NA_real_
      )
  )

coping.pcl.raw.id %>%
  descr(pcl.sum_score_base_raw, stats = "common")

coping.pcl.raw.id %>%
  descr(pcl.sum_score_base, stats = "common")
```

```{r coping pcl retro sum score if missigng items set to NA}
coping.pcl.raw.id <- coping.pcl.raw.id %>%
  mutate(
    pcl.sum_score_retro =
      if_else(condition = na_per_person_pcl_retro > 0,
              true = NA_real_,
              false = pcl.sum_score_retro_raw,
              missing = NA_real_
      )
  )

coping.pcl.raw.id %>%
  descr(pcl.sum_score_retro_raw, stats = "common")

coping.pcl.raw.id %>%
  descr(pcl.sum_score_retro, stats = "common")
```

```{r coping glad pcl head}
head(coping.pcl.raw.id)
```

```{r coping glad pcl summary}
summarytools::dfSummary(
  coping.pcl.raw.id,
  graph.col = F,
  valid.col = F,
  labels.col = F)
```

@@

# Calulate total score
phq.scored_items_retro <- scoreItems(keys = phq.items_key_retro,
                                     items = coping.phq.raw.id[phq.items_retro],
                                     totals = TRUE, 
                                     missing = TRUE, 
                                     impute = 'none', 
                                     min = 0, 
                                     max = 3)
# Add in column to tibble
coping.phq.raw.id$phq.sum_score_retro_raw <- phq.scored_items_retro$scores

# Look at values
coping.phq.raw.id %>%
  descr(phq.sum_score_retro_raw,
        stats = "common"
  )
```

@@

# Calulate total score
phq.scored_items_base <- scoreItems(keys = phq.items_key_base,
                                    items = coping.phq.raw.id[phq.items_base],
                                    totals = TRUE, 
                                    missing = TRUE, 
                                    impute = 'none', 
                                    min = 0, 
                                    max = 3)
# Add in column to tibble
coping.phq.raw.id$phq.sum_score_base_raw <- phq.scored_items_base$scores

# Look at values
coping.phq.raw.id %>%
  descr(phq.sum_score_base_raw,
        stats = "common"
  )
```

@@

retrospective
```{r coping phq retro missingness}
coping.phq.raw.id <- coping.phq.raw.id %>%
  mutate(
    na_per_person_phq_retro =         # variable for NA per person
      rowSums(
        is.na(.[phq.items_retro])
      )
  )

coping.phq.raw.id %>%
  freq(na_per_person_phq_retro, cumul = F) #have a look at the frequency
```

```{r coping phq retro missingness 8 items}
coping.phq.raw.id <- coping.phq.raw.id %>%
  mutate(
    phq.missing_only_suicide_item_retro = 
      if_else(
        condition = na_per_person_phq_retro == 1 & 
          is.na(phq.dead_hurting_thoughts_retro_numeric), 
        true = 1,
        false = 0,
        missing = NA_real_
      )
  )

coping.phq.raw.id %>%
  freq(phq.missing_only_suicide_item_retro,
       cumul = F)
```

baseline
```{r coping phq base missingness}
coping.phq.raw.id <- coping.phq.raw.id %>%
  mutate(
    na_per_person_phq_base =         # variable for NA per person
      rowSums(                       
        is.na(.[phq.items_base])
      )
  )

coping.phq.raw.id %>%
  freq(na_per_person_phq_base, cumul = F) #have a look at the frequency
```

We need to identify those who have all items APART from the suicide ideation item - to still include these individuals. 
```{r coping phq base missingness 8 items}
coping.phq.raw.id <- coping.phq.raw.id %>%
  mutate(
    phq.missing_only_suicide_item_base = 
      if_else(
        condition = na_per_person_phq_base == 1 & 
          is.na(phq.dead_hurting_thoughts_base_numeric), 
        true = 1,
        false = 0,
        missing = NA_real_
      )
  )

coping.phq.raw.id %>%
  freq(phq.missing_only_suicide_item_base,
       cumul = F)
```

```{r coping phq base sum score if missigng items set to NA}
coping.phq.raw.id <- coping.phq.raw.id %>%
  mutate(
    phq.sum_score_base =
      if_else(condition = na_per_person_phq_base > 0,
              true = NA_real_,
              false = phq.sum_score_base_raw,
              missing = NA_real_
      )
  )

coping.phq.raw.id %>%
  descr(phq.sum_score_base_raw, stats = "common")

coping.phq.raw.id %>%
  descr(phq.sum_score_base, stats = "common")
```

8 items
```{r phq base sum score if missigng items set to NA - 8 items}
coping.phq.raw.id <- coping.phq.raw.id %>%
  mutate(
    phq.sum_score_8items_base =
      if_else(condition = na_per_person_phq_base > 1 &
                phq.missing_only_suicide_item_base == 1,
              true = NA_real_,
              false = phq.sum_score_base_raw,
              missing = NA_real_
      )
  )

coping.phq.raw.id %>%
  descr(phq.sum_score_8items_base, stats = "common")
```

```{r coping phq retro sum score if missigng items set to NA}
coping.phq.raw.id <- coping.phq.raw.id %>%
  mutate(
    phq.sum_score_retro =
      if_else(condition = na_per_person_phq_retro > 0,
              true = NA_real_,
              false = phq.sum_score_retro_raw,
              missing = NA_real_
      )
  )

coping.phq.raw.id %>%
  descr(phq.sum_score_retro_raw, stats = "common")

coping.phq.raw.id %>%
  descr(phq.sum_score_retro, stats = "common")
```

8 items
```{r phq retro sum score if missigng items set to NA - 8 items}
coping.phq.raw.id <- coping.phq.raw.id %>%
  mutate(
    phq.sum_score_8items_retro =
      if_else(condition = na_per_person_phq_retro > 1 &
                phq.missing_only_suicide_item_retro == 1,
              true = NA_real_,
              false = phq.sum_score_retro_raw,
              missing = NA_real_
      )
  )

coping.phq.raw.id %>%
  descr(phq.sum_score_8items_retro, stats = "common")
```

```{r coping glad phq head}
head(coping.phq.raw.id)
```

```{r coping glad phq summary}
summarytools::dfSummary(
  coping.phq.raw.id,
  graph.col = F,
  valid.col = F,
  labels.col = F)
```

@@

# Calulate total score
ocir.scored_items_retro <- scoreItems(keys = ocir.items_key_retro,
                                     items = coping.ocir.raw.id[ocir.items_retro],
                                     totals = TRUE, 
                                     missing = TRUE, 
                                     impute = 'none', 
                                     min = 0, 
                                     max = 4)
# Add in column to tibble
coping.ocir.raw.id$ocir.sum_score_retro_raw <- ocir.scored_items_retro$scores

# Look at values
coping.ocir.raw.id %>%
  descr(ocir.sum_score_retro_raw,
        stats = "common"
  )
```

@@

# Calulate total score
ocir.scored_items_base <- scoreItems(keys = ocir.items_key_base,
                                    items = coping.ocir.raw.id[ocir.items_base],
                                    totals = TRUE, 
                                    missing = TRUE, 
                                    impute = 'none', 
                                    min = 0, 
                                    max = 4)
# Add in column to tibble
coping.ocir.raw.id$ocir.sum_score_base_raw <- ocir.scored_items_base$scores

# Look at values
coping.ocir.raw.id %>%
  descr(ocir.sum_score_base_raw,
        stats = "common"
  )
```

@@

retrospective
```{r coping ocir retro missingness}
coping.ocir.raw.id <- coping.ocir.raw.id %>%
  mutate(
    na_per_person_ocir_retro =         # variable for NA per person
      rowSums(
        is.na(.[ocir.items_retro])
      )
  )

coping.ocir.raw.id %>%
  freq(na_per_person_ocir_retro, cumul = F) #have a look at the frequency
```

baseline
```{r coping ocir base missingness}
coping.ocir.raw.id <- coping.ocir.raw.id %>%
  mutate(
    na_per_person_ocir_base =         # variable for NA per person
      rowSums(                       
        is.na(.[ocir.items_base])
      )
  )

coping.ocir.raw.id %>%
  freq(na_per_person_ocir_base, cumul = F) #have a look at the frequency
```

```{r coping ocir base sum score if missigng items set to NA}
coping.ocir.raw.id <- coping.ocir.raw.id %>%
  mutate(
    ocir.sum_score_base =
      if_else(condition = na_per_person_ocir_base > 0,
              true = NA_real_,
              false = ocir.sum_score_base_raw,
              missing = NA_real_
      )
  )

coping.ocir.raw.id %>%
  descr(ocir.sum_score_base_raw, stats = "common")

coping.ocir.raw.id %>%
  descr(ocir.sum_score_base, stats = "common")
```

```{r coping ocir retro sum score if missigng items set to NA}
coping.ocir.raw.id <- coping.ocir.raw.id %>%
  mutate(
    ocir.sum_score_retro =
      if_else(condition = na_per_person_ocir_retro > 0,
              true = NA_real_,
              false = ocir.sum_score_retro_raw,
              missing = NA_real_
      )
  )

coping.ocir.raw.id %>%
  descr(ocir.sum_score_retro_raw, stats = "common")

coping.ocir.raw.id %>%
  descr(ocir.sum_score_retro, stats = "common")
```

```{r coping glad ocir head}
head(coping.ocir.raw.id)
```

```{r coping glad ocir summary}
summarytools::dfSummary(
  coping.ocir.raw.id,
  graph.col = F,
  valid.col = F,
  labels.col = F)
```
